### 2015-01-19 src/introduction.Rnw
update

Finally, with bytecode~\footnote{A \textit{do faster} approach for eliminating
the compilation step to gain execution speed} based mutation engines such as
PIT~\cite{pitest} and Javalanche~\cite{javalanche} becoming common in both
development and research (e.g. \cite{zhang2013ase}, \cite{gopinath2014code},
and \cite{inozemtseva2014coverage}), operators based on source code
modification are no longer directly applicable, and their equivalents in
bytecode need to be identified and compared with other approaches.

@@

For this study, we experimented five classic mutation selection
techniques: Constrained \cite{wong1995reducing}, E-Selective
\cite{offutt1996anexperimental}, Javalanche \cite{javalanche},
Variable Reduction~\cite{namin2006finding} and N-Selection
\cite{offutt1993experimental}, along with two sampling approaches:
element based \cite{zhang2013ase} and operator based sampling
\cite{wong1995reducing}. We compare test effectiveness of each of techniques
with pure random sampling. Our results show that in most cases there is no
statistically significant benefit for mutation selection techniques. Moreover,
in cases with statistically significant benefit, the gain is so low that is
essentially negligible.

>>>>

Finally, with bytecode~\footnote{A \textit{do faster} approach for eliminating
the compilation step to gain execution speed} based mutation engines such as
PIT~\cite{pitest} and Javalanche~\cite{schuler2009efficient} becoming common in both
development and research (e.g. \cite{zhang2013ase}, \cite{gopinath2014code},
and \cite{inozemtseva2014coverage}), operators based on source code
modification are no longer directly applicable, and their equivalents in
bytecode need to be identified and compared with other approaches.

@@

For this study, we experimented five classic mutation selection
techniques: Constrained \cite{wong1995reducing}, E-Selective
\cite{offutt1996anexperimental}, Javalanche \cite{schuler2009efficient},
Variable Reduction~\cite{namin2006finding} and N-Selection
\cite{offutt1993experimental}, along with two sampling approaches:
element based \cite{zhang2013ase} and operator based sampling
\cite{wong1995reducing}. We compare test effectiveness of each of techniques
with pure random sampling. Our results show that in most cases there is no
statistically significant benefit for mutation selection techniques. Moreover,
in cases with statistically significant benefit, the gain is so low that is
essentially negligible.
